CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-10 paper.Rmd
Updated example.

# (4) Run the PFUAggDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"))
```

>>>>

# (4) Run the PFUAggDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"))

# Look at the PSUT data frame
psut <- targets::tar_read(PSUT)
head(psut)
# Each column of the psut data frame contains matrices
psut$R[[1]]
```
